RNA-seq from 4 cell populations

### 2021-08-04 deconvolution/fans4/molec_profiling.Rmd
bug fix

```{r DE.analysis}

@@

```{r DE2}

@@

## Plots of top differentially expressed genes
```{r DE.marker_genes, fig.width=15, fig.height=40}

@@

```{r compare.celltypes}
zenith_gsa = function (fit, coefs, geneSets, n_genes_min = 10, n_genes_max=1000,...){

@@

coefTests = colnames(coef(fitBasic))[c(1, 7:9)]
df_zenith = zenith_gsa(fitBasic[fitBasic$Amean > 0,], coefTests, geneSets_GO, inter.gene.cor=0.01)

@@

M = matrix(-log10(df$p.greater), nrow=nrow, ncol=ncol,dimnames=list(unique(df$coef), unique(df$Geneset)), byrow=TRUE)

hcl_col = hclust(dist(M), method="ward.D")
df$coef = factor(df$coef, rownames(M)[hcl_col$order])

hcl_row = hclust(dist(t(M)), method="ward.D")
# df$Geneset = factor(df$Geneset, colnames(M)[hcl_row$order])
df$Geneset = factor(df$Geneset, cls)
df$label = ifelse(df$FDR < 0.05, '*', '')

>>>>

```{r DE.analysis}
index = combn(nlevels(info$CellType),2)

@@

```{r DE2}
index = combn(nlevels(info$CellType),2)

@@

## Plots of top differentially expressed genes
```{r DE.marker_genes, fig.width=15, fig.height=40}
index = combn(nlevels(info$CellType),2)

@@

```{r compare.celltypes, fig.width=8, fig.height=12}
zenith_gsa = function (fit, coefs, geneSets, n_genes_min = 10, n_genes_max=1000,...){

@@

coefTests = c('GABA_vs_GLU', 'GABAGLU_vs_Other', 'GLU_vs_Other', 'GABA_vs_Other', 'MgAs_vs_Other', 'Olig_vs_Other')
df_zenith = zenith_gsa(fitBasic[fitBasic$Amean > 0,], coefTests, geneSets_GO)
#, inter.gene.cor=0.01)

@@

# M = matrix(-log10(df$p.greater), nrow=nrow, ncol=ncol,dimnames=list(unique(df$coef), unique(df$Geneset)), byrow=TRUE)

# M = matrix(-log10(df$p.greater), nrow=nrow, ncol=ncol, byrow=TRUE)
# rownames(M) = unique(df$coef)
# colnames(M) = unique(df$Geneset)

# Heatmap(t(M), col = colorRampPalette(c("white", "red"))(100))

# hcl_col = hclust(dist(M), method="ward.D2")
# df$coef = factor(df$coef, rownames(M)[hcl_col$order])

# hcl_row = hclust(dist(t(M)), method="ward.D2")
# df$Geneset = factor(df$Geneset, colnames(M)[hcl_row$order])
df$Geneset = factor(df$Geneset, cls)
df$label = ifelse(df$FDR < 0.05, '*', '')
